---
title: '401'
author: "YZL"
date: "9/21/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r}
library(tidyquant)
library(readr)
library(dplyr)
library(tidyverse)
library(car)
library(lubridate)
library(stargazer)
library(ggplot2)
library(zoo)
library(gridExtra)
```



```{r}
all_derived_eps <- read.csv("/Users/yizhenglu/Downloads/Stock essay/quartely_all_eps.csv")
```



```{r}
all_derived_eps<-all_derived_eps%>%
  mutate(year =year(Report.Date))
```

```{r}
eps_2015<-all_derived_eps%>%
  filter(year>=2015)
```




```{r}
daily_price <- read.csv("/Users/yizhenglu/Downloads/Stock essay/daily_price.csv")
daily_price<-daily_price%>%
  mutate(year =year(Date))
daily_price_2014<-daily_price%>%
  filter(year>=2014)
```
```{r}
#Calculate	a	3-period	relative	strength	index	(RSI)	off	the	Close	price 
RSI_Close	<- RSI(daily_price_2014[,c("Close")],	n	= 3)
#	5-period	exponential	moving	average	(EMA)
EMA_Close	<- EMA(daily_price_2014[,c("Close")],	n	= 5)
# difference	between	the	Close	price	and	our	5-period	EMA
EMAcross_Close	<- daily_price_2014[,c("Close")]	- EMA_Close

#Calculate	a	MACD	with	standard	parameters
macd <- MACD(daily_price_2014[,c("Close")], nFast=12, nSlow=26,
               nSig=9, percent=FALSE)
#Grab	just	the	signal	line	to	use	as	our	indicator
MACDsignal	<- macd[,	2]
```

```{r}
SMI<-SMI(daily_price_2014[,c("High","Low","Close")], n = 13, nFast = 2, nSlow = 25, nSig = 9)
SMI	<- SMI[,	1]
```


```{r}
#Commodity	Channel	Index	with	standard	parameters
CCI	<- CCI(daily_price_2014[,c("High","Low","Close")],	n	= 14)
#Chande Momentum Oscillator	with	standard	parameters
CMO	<- CMO(daily_price_2014[,c("Close")],	n	= 14)
ROC	<- ROC(daily_price_2014[,c("Close")],	n	= 2)
```
```{r}
daily_ADX  <- ADX(daily_price_2014[,c("High","Low","Close")],n=14)
obv <- OBV(daily_price_2014[,"Close"], daily_price_2014[,"Volume"])
stochWPR<- WPR(daily_price_2014[,c("High","Low","Close")],n=14)
  
```
```{r}
#predictors
daily_price_2014<- mutate(daily_price_2014, PriceChange = Close - lag(Close))
```



```{r}
cbind_daily<- cbind(daily_price_2014,RSI_Close,EMAcross_Close,MACDsignal,SMI,CCI,CMO,ROC,daily_ADX,obv,stochWPR)
```




```{r}
cbind_daily_2015<-cbind_daily%>%
  filter(year>=2015)
```


```{r}
cbind_daily_2015$Date <- as.Date(cbind_daily_2015$Date)
```



```{r}
quarter_price_2015<-cbind_daily_2015%>%
  select(Ticker,Date,Open,Low,High,Close,Adj..Close,Volume,Shares.Outstanding,year,ADX,obv,stochWPR)%>%
  filter(Date ==as.Date("2015-03-31")|Date ==as.Date("2015-06-30")|Date ==as.Date("2015-09-30")|Date ==as.Date("2015-12-31")|Date ==as.Date("2016-03-31")|Date ==as.Date("2016-06-30")|Date ==as.Date("2016-09-30")|Date ==as.Date("2016-12-30")|Date ==as.Date("2017-03-31")|Date ==as.Date("2017-06-30")|Date ==as.Date("2017-09-29")|Date ==as.Date("2017-12-29")|Date ==as.Date("2018-03-29")|Date ==as.Date("2018-06-29")|Date ==as.Date("2018-09-28")|Date ==as.Date("2018-12-31")|Date ==as.Date("2019-03-29")|Date ==as.Date("2019-06-28")|Date ==as.Date("2019-09-30")|Date ==as.Date("2019-12-31")|Date ==as.Date("2020-03-31")|Date ==as.Date("2020-06-30")|Date ==as.Date("2020-09-30"))
```

```{r}
quarter_price_2015<-quarter_price_2015%>%
  mutate(month=month(Date))
```

```{r}
quarter_price_2015 <-quarter_price_2015%>%
  mutate(Date =case_when(month=="3"~ "Q1"))
quarter_price_2015$Date[quarter_price_2015$month ==6] <- "Q2"
quarter_price_2015$Date[quarter_price_2015$month ==9] <- "Q3"
quarter_price_2015$Date[quarter_price_2015$month ==12] <- "Q4"
quarter_price_2015<-select(quarter_price_2015,-c("month"))
```

```{r}
quarter_price_2015$Fiscal.Period<-quarter_price_2015$Date
quarter_price_2015<-select(quarter_price_2015,-c("Date"))
```

```{r}
oil_price <- read.csv("/Users/yizhenglu/Downloads/Stock essay/end_quarter/oil_price.csv")
oil_price<-oil_price%>%
  mutate(year =year(DATE))%>%
  mutate(month =month(DATE))
```
#Oil Price
```{r}
oil_price <-oil_price%>%
  mutate(Fiscal.Period =case_when(month=="1"~ "Q1"))
oil_price$Fiscal.Period[oil_price$month ==4] <- "Q2"
oil_price$Fiscal.Period[oil_price$month ==7] <- "Q3"
oil_price$Fiscal.Period[oil_price$month ==10] <- "Q4"

```
```{r}
oil_price$Oil_price_quarter <- oil_price$DCOILWTICO
oil_price<-select(oil_price,-c(2))
oil_price<-select(oil_price,-c(1,3))
```

#Natural Rate of Unemployment (Long-Term)
```{r}
UNRATE <- read.csv("/Users/yizhenglu/Downloads/Stock essay/end_quarter/UNRATE.csv")
UNRATE<-UNRATE%>%
  mutate(year =year(DATE))%>%
  mutate(month =month(DATE))

UNRATE <-UNRATE%>%
  mutate(Fiscal.Period =case_when(month=="1"~ "Q1"))
UNRATE$Fiscal.Period[UNRATE$month ==4] <- "Q2"
UNRATE$Fiscal.Period[UNRATE$month ==7] <- "Q3"
UNRATE$Fiscal.Period[UNRATE$month ==10] <- "Q4"

UNRATE<-select(UNRATE,-c(1,4))

```

#CPI
```{r}

CPI_rate <- read.csv("/Users/yizhenglu/Downloads/Stock essay/end_quarter/CPI.csv")
CPI_rate<-CPI_rate%>%
  mutate(year =year(DATE))%>%
  mutate(month =month(DATE))

CPI_rate <-CPI_rate%>%
  mutate(Fiscal.Period =case_when(month=="1"~ "Q1"))
CPI_rate$Fiscal.Period[CPI_rate$month ==4] <- "Q2"
CPI_rate$Fiscal.Period[CPI_rate$month ==7] <- "Q3"
CPI_rate$Fiscal.Period[CPI_rate$month ==10] <- "Q4"

CPI_rate$CPI_Quarter <- CPI_rate$CPALTT01USM657N
CPI_rate<-select(CPI_rate,-c(1,2,4))

```



#exchange rates
```{r}
ex_rate<- read.csv("/Users/yizhenglu/Downloads/Stock essay/end_quarter/exchange_rate.csv")

ex_rate<-ex_rate%>%
  mutate(year =year(DATE))%>%
  mutate(month =month(DATE))

ex_rate <-ex_rate%>%
  mutate(Fiscal.Period =case_when(month=="1"~ "Q1"))
ex_rate$Fiscal.Period[ex_rate$month ==4] <- "Q2"
ex_rate$Fiscal.Period[ex_rate$month ==7] <- "Q3"
ex_rate$Fiscal.Period[ex_rate$month ==10] <- "Q4"

ex_rate$ex_rate <- ex_rate$DEXCHUS

ex_rate<-select(ex_rate,-c(1,2,4))
```



#GDP
```{r}
GDP<- read.csv("/Users/yizhenglu/Downloads/Stock essay/end_quarter/GDP.csv")

GDP<-GDP%>%
  mutate(year =year(DATE))%>%
  mutate(month =month(DATE))

GDP <-GDP%>%
  mutate(Fiscal.Period =case_when(month=="1"~ "Q1"))
GDP$Fiscal.Period[GDP$month ==4] <- "Q2"
GDP$Fiscal.Period[GDP$month ==7] <- "Q3"
GDP$Fiscal.Period[GDP$month ==10] <- "Q4"

GDP$GDP <- GDP$GDP
GDP<-select(GDP,-c(1,4))
```

```{r}
Inflation<- read.csv("/Users/yizhenglu/Downloads/Stock essay/end_quarter/Inflation.csv")

Inflation<-Inflation%>%
  mutate(year =year(DATE))%>%
  mutate(month =month(DATE))

Inflation <-Inflation%>%
  mutate(Fiscal.Period =case_when(month=="1"~ "Q1"))
Inflation$Fiscal.Period[Inflation$month ==4] <- "Q2"
Inflation$Fiscal.Period[Inflation$month ==7] <- "Q3"
Inflation$Fiscal.Period[Inflation$month ==10] <- "Q4"

Inflation$Inflation <- Inflation$T10YIE
Inflation<-select(Inflation,-c(1,2,4))
```




```{r}

```

```{r}
CPI_UNRATE_Oil<-merge(CPI_rate,UNRATE, by=c("Fiscal.Period","year"))
CPI_UNRATE_Oil<-merge(oil_price,CPI_UNRATE_Oil,by=c("Fiscal.Period","year"))
CPI_UNRATE_Oil_EX<-merge(ex_rate,CPI_UNRATE_Oil,by=c("Fiscal.Period","year"))
CPI_UNRATE_Oil_EX_GDP <-merge(GDP,CPI_UNRATE_Oil_EX,by=c("Fiscal.Period","year"))
CPI_UNRATE_Oil_EX_GDP_Inf <-merge(Inflation,CPI_UNRATE_Oil_EX_GDP,by=c("Fiscal.Period","year"))
```
```{r}
#Combine year and Fiscal.Period for graph
CPI_UNRATE_Oil_EX_GDP_Inf<-within(CPI_UNRATE_Oil_EX_GDP_Inf, YQ <- paste(year, Fiscal.Period, sep=''))

```


```{r}
CPI_UNRATE_Oil_EX_GDP_Inf$YQ <- as.Date(as.yearqtr(CPI_UNRATE_Oil_EX_GDP_Inf$YQ))


plot1<-ggplot(CPI_UNRATE_Oil_EX_GDP_Inf) +
    geom_line(aes(x=YQ, y=Inflation,color="Inflation"))+
    geom_line(aes(x=YQ, y=CPI_Quarter,color="CPI"))+
    geom_line(aes(x=YQ,y=UNRATE,color="Unemployment "))+
    geom_line(aes(x=YQ,y=log(Oil_price_quarter),color="log of Oil Price "))+
    geom_line(aes(x=YQ,y=ex_rate,color="Ex_rate "))+
    ylab("Values")+
    ggtitle("Variables Trend From 2015 Q1 to 2020Q2")+
  xlab("Years and Quarter")

plot2<-ggplot(CPI_UNRATE_Oil_EX_GDP_Inf) +
  geom_line(aes(x=YQ,y=GDP,color= "GDP"))+
  ylab("Values")+
  ggtitle("GDP Trend From 2015 Q1 to 2020Q2")+
  xlab("Years and Quarter")
grid.arrange(plot1, plot2)
  
```


```{r}
eps_2015_com<-merge(eps_2015,CPI_UNRATE_Oil_EX_GDP_Inf,by=c("Fiscal.Period","year"))
```
```{r}
complete_2015 <-merge(eps_2015_com,quarter_price_2015,by=c("Fiscal.Period","year","Ticker"))
```

```{r}
complete_2015<-select(complete_2015,-c("Publish.Date","Restated.Date"))
```



```{r}
complete_2015<-as.data.frame.matrix(complete_2015) 

```

```{r}
factors_pps<-complete_2015%>%
  select(Fiscal.Period,year,Ticker,Report.Date,Return.on.Equity, Return.on.Assets,Earnings.Per.Share..Basic,Equity.Per.Share, Inflation,GDP,           ex_rate,Oil_price_quarter,CPI_Quarter,UNRATE,Close)
```



```{r}
summary(factors_pps)
```


  In our example, if we ran a regression of price, ad and location on volume, we would get a result with an R-squared of 0.1915。 This shows that 19.15% of the variation in volume can be explained by the other variables.
  VIF measures how much of the variation in one variable is explained by the other variable.

```{r}
factors_pps_omit <- na.omit(factors_pps)

```



```{r}
#factors_pps_omit is after na.omit, the dataset is to see what factors may affect stock prices.
linear1<-lm(Close~GDP+Oil_price_quarter+ex_rate+CPI_Quarter+UNRATE+Inflation+Return.on.Assets+Return.on.Equity+Earnings.Per.Share..Basic+Equity.Per.Share,data =factors_pps_omit )
summary(linear1)
```


```{r}
summary(factors_pps_omit)
```

```{r}
#Remove year, ticker, Report.Date, Fiscal.Period
factors_pps_omit_remdouble<-factors_pps_omit%>%
  select(-c(1,2,3,4))
```





```{r}
cor(factors_pps_omit_remdouble,method = c("pearson"))
```


```{r}
library(ggcorrplot)
ggcorrplot(cor(factors_pps_omit_remdouble))+
  ggtitle("Correlation Coefficients between variables.")
```

```{r}
vif(linear1)
```

    From the correlation plot, it shows Oil_price_quarter has a high positive correlation with Inflation. The VIF function tells Oil_price_quarter has a high VIF score. This probably be problematic due to the multicolnearity issue. Therefore, I would like to drop this variable in future models.
```{r}
linear2<-lm(Close~GDP+ex_rate+CPI_Quarter+UNRATE+Inflation+Return.on.Assets+Return.on.Equity+Earnings.Per.Share..Basic+Equity.Per.Share,data =factors_pps_omit )
summary(linear2)
```
```{r}
vif(linear2)#Vif After deleting Oil_price
```

```{r}
linear3<-lm(Close~GDP+Oil_price_quarter+ex_rate+CPI_Quarter+UNRATE+Return.on.Assets+Return.on.Equity+Earnings.Per.Share..Basic+Equity.Per.Share,data =factors_pps_omit )
summary(linear3)
```
```{r}
vif(linear3) #VIF after deleting inflation
```

```{r}
stargazer(linear1, linear2,linear3, title="Regression Results",type = "text")
```

    The linear 1 shows that adjusted R2 , the model explains 19.1% of the variation on
    stock prices. The estimated coefficients of UNRATE,EVPS,ROA, GDP, and EPS are statistically significant  of significance.
    as expected,  GDP and EPS are positive impact on stock prices. However, EVPS's negative impact on stock prices.
    However, Oil_price and CPI and inflation rate are not expected because they are not statistically significant.
    Then I run a multicollinearity test among those variables. The multicollinearity test shows Oil_price and inflation rate have a strong collinearity.
    
    The linear 2 shows I removed th oil_price. Similarly, UNRATE,EVPS,ROA, GDP, and EPS are statistically significant  of significance. Furthermore, Inflation becomes statistically significant as well. However, unexpectedly, the coefficient for Inflation rate was positive.
    
    The linear 3 shows when removing inflation and keep oil_price, the GDP is statistically significant but less than the linear 2. Futhermore, oil_price becomes statistically significant as well.  Unexpectedly, the coefficient for oil_price rate was positive.
    



```{r}
#Run this when you need
#write_csv(cbind_daily_2015,"Predictions data.csv")
```




